---
title: "Output Report from Shiny Application: Linear Regression Analysis"
author: "Dongwen Luo"
---

# Data Information Output:

## Updated Data:
```{r Data_info2, echo=FALSE}
str(rslt$dat)
```

# Data Tabulate Output
```{r tabu, echo=FALSE}
print(isolate(reactiveValuesToList(tabudat)))
```

# Graph Output
```{r plot, fig.height=7, fig.width=7,  echo=FALSE}
print(isolate(reactiveValuesToList(datplt)))
```

# Modelling Output

### Data for Modelling
```{r modeldat, echo=FALSE}
str(rslt$modeldata)
```
### Model
To fit the data, we applied a *`r class(rslt$mod)[1]`* model with fixed terms *`r rslt$modterm`*. 

* ANOVA:
```{r modelanova, echo=FALSE}
print(rslt$anova)
```
* Summary:
```{r modelsummary, echo=FALSE}
print(rslt$summary)
```
* Confidence interval for parameters:
```{r modelconfint, echo=FALSE}
print(rslt$confint)
```

# Predicted Means Output

For model terms of interest, we performed some further inference.
```{r modelpredictm, fig.height=7, fig.width=7, echo=FALSE}
if (!is.null(rslt$pdmt)) {
	predictmeans(model=rslt$mod, modelterm=rslt$pdmt, pairwise=rslt$pair, atvar=rslt$atvar, 
	  adj=rslt$adj, Df=rslt$Df,plotord = rslt$morder, barplot = rslt$mptype=="bar", 
	  level=rslt$level, covariate=rslt$covvalue, trans =rslt$bkf, newwd=FALSE)
}
``` 

```{r modelcovm, fig.height=7, fig.width=7, echo=FALSE} 
print(rslt$covariatemeansplot)
``` 
# Packages for building the above output 

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
Enter file contents here
